Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-08-03 TitlePage.tex
Switch to lmodern for whole thesis
Output seems close enough (just a couple page breaks shifted). Chapter title
fonts are bolder.
Drop extra \selectfont

{\bfseries Dissertation}\\
der Mathematisch- und Naturwissenschaftlichen Fakult\"at\\
der Eberhard Karls Universit\"at T\"ubingen\\
zur Erlangung des Grades eines\\
Doktors der Naturwissenschaften\\
(Dr.\ rer.\ nat.)

>>>>

{\bfseries Dissertation}\\
der Mathematisch- und Naturwissenschaftlichen Fakult\"at\\
der Eberhard Karls Universit\"at T\"ubingen\\
zur Erlangung des Grades eines\\
Doktors der Naturwissenschaften\\
(Dr. rer. nat.)
